# p8105_hw1_lah2231
## Homework I

install.packages("palmerpenguins")

```{r, echo = FALSE}
data("penguins", package = "palmerpenguins")
#View(penguins)
head(penguins)
ncol(penguins)
```

The penguins dataset from the palmerpenguins package has `r ncol(penguins)` columns which are as follows: `r colnames(penguins)`. The different species of penguins the dataset looks at are: `r unique(penguins$species)`. They live in one of the following places or islands: `r unique(penguins$island)`. There are `r nrow(penguins)` rows. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.



```{r}
library(ggplot2)
first_plot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + labs(title="Penguin flipper vs. Penguin bill", x="Bill lenght", y="Flipper length")
print(first_plot)
ggsave("first_plot.png", plot = first_plot)
```


```{r}
library(tidyverse)

data_frame1 <- data.frame(
  Random_samples_normal_data = rnorm(10, mean = 0, sd = 1),
  Character_vector = c ("c", "h", "a", "r", "a", "c", "t", "e", "r", "v"),
  Factor_vector = c("low", "medium", "high", "low", "high", "low", "medium", "high", "low", "high")
)

data_frame1$Logical_vector_greater_0 <- data_frame1$Random_samples_normal_data > 0

mean(data_frame1$Random_samples_normal_data)
mean(data_frame1$Character_vector)
mean(data_frame1$Factor_vector)
mean(data_frame1$Logical_vector_greater)

print(data_frame1)
```

random_sample 












